Supplementary Information: Tropical tree drought sensitivity is jointly shaped by drought characteristics, species adaptations, and individual microenvironments

### 2025-06-19 doc/supplementary_information.Rmd
plot of residuals added to SI
updated SI file with fig captions

@@

![**Figure S10:** Testing correlations of variables across all individuals](display/cond_dep_alltrees.png)

@@

![**Figure S11:** Testing correlations for DBH $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_dbh_twi.png)

![**Figure S12:** Testing correlations for CII $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_cii_twi.png)

@@

## Visualising sensitivity with predictors

![](display/sens_var_rels.png)

@@

![](display/FigSI_TPI_preds.png)

@@

![](display/Fig4_tpi_3yrs.png)

>>>>

## Raw sensitivity and residuals with predictors

![**Figure S10:** Distribution of raw sensitivity values across years and their relationship with DBH, CII and TWI. Lines are linear model fits.](display/sens_var_rels.png)

![**Figure S11:** Distribution of residuals of species intercept models of sensitivity and their relationship with scaled DBH, TWI and CII and deciduousness. Species intercept model results are reported in main text.](display/residuals.png)

@@

![**Figure S12:** Testing correlations of variables across all individuals](display/cond_dep_alltrees.png)

@@

![**Figure S13:** Testing correlations for DBH $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_dbh_twi.png)

![**Figure S14:** Testing correlations for CII $\perp\!\!\!\perp$ TWI by species](display/explore/cond_dep_cii_twi.png)

@@

@@

![**Figure S15:** Correlation of modelled species sensitivities with Topographic Position Index](display/FigSI_TPI_preds.png)

@@

![**Figure S16:** Model results from Bayesian causal model of sensitivity as a function of DBH, CII and TPI.](display/Fig4_tpi_3yrs.png)
